### 2024-10-16 texts/sup_materials.tex
include founder death/museum name interaction in sup materials

% Created 2024-09-30 ma 14:08
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\subsection*{Alternative competition specifications}

@@

As private museum closing might depend on particular country- or region-level factors, table \ref{tbl:t_reg_coxph_reg} shows a number of Cox Proportional Hazard regression models results with different sets of dummy variables.
In particular, dummy variables are added for UN region code (with a minor modification of splitting the Americas into North and Latin America according to the UN subregion codes and reference category of Africa), the UN subregion code itself (with reference category of Northern America), as well as country level (with reference category of United States).
For models with country-dummies, country-level private museum density variables are removed as the high collinearity led to unreasonably high country-dummy estimates.
As many countries and some UN subregions have too few private museums for the model to converge correctly, the dataset is reduced to include only regions or countries with 10 or more private museums (in the case of country2, 15 private museums).
To identify whether any change in coefficients is due to addition of variables or exclusion of cases, a separate model with the same restricted sample but without region/country dummies is included.

@@

Figure \ref{fig:p_vrblcvrg_ratio} shows the variable coverage by whether a museum is open or closed at the status of data collection (2020-2022).
Not only is coverage on most variables far from complete, which would already make it difficult to construct indicators of them, but variable coverage is substantially worse for closed museums than for open museums, especially variables related to the collection, operation, relations to other actors and social media.
In principle it is possible to treat absence of evidence as evidence of absence, and assume that not measuring the presence of e.g. temporary exhibitions, educational events, restaurants or cooperations means that these are absent.

>>>>

% Created 2024-10-16 wo 12:28
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\subsection*{Alternative founder death specification}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep 27 17:51:20 2024
\begin{table}[ht]
\centering
\begin{tabular}{rD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{Recent death length} & \multicolumn{1}{l}{Recently dead} & \multicolumn{1}{l}{Long dead}\\ 
 \hline
   1 & .97 \; (1.02) & .19 \; (0.46) \\ 
    2 & 1.37 \; (0.61)^{*} & -.16 \; (0.55) \\ 
    3 & 1.06 \; (0.61) & -.09 \; (0.55) \\ 
    4 & .83 \; (0.61) & -.02 \; (0.55) \\ 
    5 & .62 \; (0.61) & .07 \; (0.55) \\ 
    6 & .50 \; (0.61) & .13 \; (0.55) \\ 
    7 & .87 \; (0.49) & -.51 \; (0.75) \\ 
    8 & .80 \; (0.49) & -.45 \; (0.75) \\ 
    9 & .91 \; (0.46)^{*} & -1.11 \; (1.03) \\ 
   10 & .83 \; (0.46) & -1.03 \; (1.03) \\ 
   11 & .78 \; (0.46) & -.98 \; (1.03) \\ 
   12 & .71 \; (0.46) & -.90 \; (1.03) \\ 
   \hline
\end{tabular}
\caption{Cox PH regression results with different death configurations} 
\label{tbl:t_reg_coxph_deathcfg}
\end{table}

It is possible to construct an alternative measure of founder death by partitioning the time after the death in a short-term and long-term period; the short-term period might then capture the disruption by the founder, whereas the long-term period would only be reached by museums who have successfully acquired alternative funding models and are hence relatively viable.
However, the choice of choosing a cut-off point between the short- and long-term periods is relatively arbitrary.

Table \ref{tbl:t_reg_coxph_deathcfg} shows coefficients of both periods with different cut-off points.
While the coefficient in the short-term period is consistently higher than both the overall death coefficient and the long-term period coefficients, so far the evidence is inconclusive as only few cases are statistically significant\footnote{P-values are also not adjusted for multiple tests}.
Furthermore, such a shock passes quickly relative to the predicted median lifetime of museums of 52 years, thus "giving" the founder death little time to lead to many museum closures. 
Considering the raw numbers underlying the death effect estimates illustrates the uncertainty involved in determining the effect of the death of the founder on closing: 
While 47 private museums have seen the death of their founders, only 3 of these have closed in the following 5 years; given such low numbers it cannot be ruled out that the statistical significance in a few configurations of founder death time results from random fluctuations rather than an underlying pattern.
\subsection*{Interaction of Founder name in Museum name and founder death}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Sep 30 14:43:50 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_founder\_name\_death\_int}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & -.02 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.12 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .73 \; (0.75) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .21 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.47 \; (0.54) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.08 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .19 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .48 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .09 \; (0.29) \\ 
   & Founder name in Museumm name * Founder died &  & -.62 \; (0.90) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .64 \; (0.34) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .27 \; (0.08)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.59 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .41 \; (0.29) \\ 
   \hline
 & Museums & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 \\ 
   & Closures & 68 & 68 \\ 
   & log. Likelihood & -339.68 & -339.46 \\ 
   & AIC & 711.35 & 712.92 \\ 
   & BIC & 746.87 & 750.65 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
\end{tabular}
\caption{Cox PH regression models with additional specifications} 
\label{tbl:t_reg_coxph_addgns}
\end{table}

While private museums generally do not experience a significantly higher risk of closing after the death of their founders, such effect might be present for a subgroup.
The most likely candidate for this would be Museums whose name include the name of the founder, as including the founder name in the museum might indicate disproportionate commitment by the founder (which would be absent after their death) as well as disincentivize third parties to contribute.
To investigate this possibility, an interaction between Founder death and inclusion of Founder name in museum name is added, results are presented in table \ref{tbl:t_reg_coxph_addgns}.
As both the main effects and the interaction are not significant, the effect of the founder's death on a musuem's closing risk does not significantly differ between museums which do include their founder's name in their name and those who do not. 
\subsection*{Alternative competition specifications}

@@

As private museum closing might depend on particular country- or region-level factors, table \ref{tbl:t_reg_coxph_reg} shows a number of Cox Proportional Hazard regression models results with different sets of dummy variables.
In particular, dummy variables are added for UN region code (with a minor modification of splitting the Americas into North and Latin America according to the UN subregion codes and reference category of Africa), the UN subregion code itself (with reference category of Northern America), as well as country level (with reference category of United States).
For models with country-dummies, country-level private museum density variables are removed as the high collinearity led to unreasonably high country-dummy estimates.
As many countries and some UN subregions have too few private museums for the model to converge correctly, the dataset is reduced to include only regions or countries with 10 or more private museums.
To identify whether any change in coefficients is due to addition of variables or exclusion of cases, a separate model with the same restricted sample but without region/country dummies is included.

@@

Figure \ref{fig:p_vrblcvrg_ratio} shows the variable coverage by whether a museum is open or closed at the status of data collection (2020-2022).
Not only is coverage on most variables far from complete, which would already make it difficult to construct indicators of them, but variable coverage is substantially worse for closed museums than for open museums, especially for variables related to the collection, operation, relations to other actors and social media.
In principle it is possible to treat absence of evidence as evidence of absence, and assume that not measuring the presence of e.g. temporary exhibitions, educational events, restaurants or cooperations means that these are absent.
